---
title: "cyung25_OriginalHomeworkCode_05"
author: "Charles Yung"
date: "`r Sys.Date()`"
output: html_document
---

`CM: I think it would be helpful to add some context to the HW, like including the actual questions so it's easier to understand what your code is supposed to do`

```{r}
## To answer question 1, Begin by loading dataset in.
library(curl)
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN588_Fall23/KamilarAndCooperData.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)
## Next we transform the relevant columns (Home Range, and Body Mass). Then we plot the model.
d$log_HomeRange <- log(d$HomeRange_km2)
d$log_BodyMassF <- log(d$Body_mass_female_mean)
d_clean <- na.omit(d[, c("log_HomeRange", "log_BodyMassF")])
model <- lm(data = d_clean, log_HomeRange ~ log_BodyMassF)
coef(model)
summary(model)
summary(model)$coefficients
## For the linear regression of log HomeRange and log BodyMassF, the estimated intercept is -9.441 and the estimated slope is 1.036. This means that log body mass increases by the slope value. The intercept is the value of the Log home range when the log BodyMassF is 0. 
```

`CM: Code looks great! I would suggest breaking down the visualization result visualization so the viewer doesn't get hit with a wall of results that are hard to interpret. By this I mean having the coef() and summary() in different R chunks`

```{r}
set.seed(1)
set <- NULL ## dummy variable to hold 1000 results
n <- 1000
boot_coefs <- matrix(NA, nrow = n, ncol = 2) ## account for number of columns: the intercept and slope
for (i in 1:n_boot) { #CM: n_boot variable appears to not be previously defined, did you mean n?
  sample_indices <- sample(1:nrow(d_clean), replace = TRUE)
  sample_data <- d_clean[sample_indices, ]
  boot_model <- lm(log_HomeRange ~ log_BodyMassF, data = sample_data)
  boot_coefs[i, ] <- coef(boot_model) 
}
colnames(boot_coefs) <- c ("Intercept", "Slope") # I would try to show the mean of the beta coefficients to show people that your code is working as it should. Something like the like I added at the below
mean(boot_coefs[,2]) #CM: my addition
boot_se <- apply(boot_coefs, 2, sd) # CM: Interesting approach using apply() 
print(boot_se)
boot_ci <- apply(boot_coefs, 2, quantile, probs = c(0.025, 0.975))
print(boot_ci) 

## standard errors of the linear model <- CM: do you mean the original model?
lm_se <- summary(model)$coefficients[, "Std. Error"]

## confidence intervals of the linear model
lm_ci <- confint(model)

## Combine all in a table <- CM: I like the idea of putting them all in a table for easier visualization but definitely make sure that you're getting the values of the slope correct
comparison <- data.frame(
  Parameter = c("Intercept", "Slope"),
  SE_lm = lm_se,
  SE_boot = boot_se,
  CI_lm_lower = lm_ci[,1],
  CI_lm_upper = lm_ci[,2],
  CI_boot_lower = boot_ci[1,],
  CI_boot_upper = boot_ci[2,]
)

print(comparison) # CM: This is just nitpicking. The table is super useful but it might be too wide. I'd suggest looking into the pivot_wide() function to make it into the longer format, having Intercept and Slope the columns instead.

##Writeup: My standard error values from the bootstrap are slightly smaller than the standard errors from the linear model (intercept beta 0 bootstrap is 0.61 compared to 0.67, beta 1 slope is 0.079 compared to 0.085). Concerning the confidence intervals, the bootstrap beta 0 intercept values and beta 1 slope values are similar, showing the linear model estimates are reliable. 

#CM: I would include these comments and reflections outside of the R chunk

## Charles' Comment: Going over this I feel like I have the majority of the code down, but I could use some advice on how to make my code more organized. Furthermore, if there are any missing equations or functions I need, please let me know as I check again!

```

`CM: I think we have very similar results so that makes me think that we're both on the right track! I think a major improvement to your work would be to break everything down in more digestible code chunks so it's easier for people to understand.`
